---
title: "Final set"
author: "Aniqa Tasnim Oishi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading required libraries

```{r}
library(dplyr)
library(skimr)
library(ggplot2)
library(lubridate)
library(tm)
library(SnowballC)
library(wordcloud)
library(stringr)
library(knitr)
library(kableExtra)
library(RColorBrewer)
library(syuzhet)
library(multcomp)
```

#Part-A Analysis
## Reading Data into R and preliminary data cleaning

```{r}
file_path <- "/Users/aniqatasnimoishi/Downloads/UniAdelaide/2024-T2/Research-A/Data/final_data_20-23.csv"

final_data <- read.csv(file_path, fileEncoding = "latin1")
final_data <- final_data %>% filter(FOI_TEXT != "")
final_data <- final_data %>% filter(MANUFACTURER_D_NAME != "")
final_data <- final_data %>% filter(BRAND_NAME != "")
final_data_clean <- subset(final_data, select = -c(MANUFACTURER_CONTACT_T_NAME, MANUFACTURER_CONTACT_F_NAME, MANUFACTURER_CONTACT_L_NAME, MANUFACTURER_CONTACT_STREET_1, MANUFACTURER_CONTACT_STREET_2, MANUFACTURER_CONTACT_CITY, MANUFACTURER_CONTACT_STATE, MANUFACTURER_CONTACT_ZIP_CODE, MANUFACTURER_CONTACT_ZIP_EXT, MANUFACTURER_CONTACT_COUNTRY, MANUFACTURER_CONTACT_POSTAL, MANUFACTURER_CONTACT_PCITY, MANUFACTURER_CONTACT_PLOCAL, MANUFACTURER_G1_NAME, MANUFACTURER_G1_STREET_1, MANUFACTURER_G1_STREET_2, MANUFACTURER_G1_CITY, MANUFACTURER_G1_STATE_CODE, MANUFACTURER_G1_ZIP_CODE, MANUFACTURER_G1_COUNTRY_CODE, MANUFACTURER_G1_POSTAL_CODE, MANUFACTURER_D_ADDRESS_1, MANUFACTURER_D_ADDRESS_2, MANUFACTURER_D_CITY, MANUFACTURER_D_STATE_CODE, MANUFACTURER_D_ZIP_CODE, MANUFACTURER_D_ZIP_CODE_EXT, MANUFACTURER_D_COUNTRY_CODE, MANUFACTURER_D_POSTAL_CODE, EVENT_KEY, NUMBER_DEVICES_IN_EVENT, NUMBER_PATIENTS_IN_EVENT, MANUFACTURER_CONTACT_EXTENSION, DISTRIBUTOR_NAME, DISTRIBUTOR_ADDRESS_1, DISTRIBUTOR_ADDRESS_2, DISTRIBUTOR_CITY, DISTRIBUTOR_STATE_CODE, DISTRIBUTOR_ZIP_CODE, DISTRIBUTOR_ZIP_CODE_EXT, REPORT_TO_MANUFACTURER, MANUFACTURER_NAME, MANUFACTURER_ADDRESS_1, MANUFACTURER_ADDRESS_2, MANUFACTURER_CITY, MANUFACTURER_STATE_CODE, MANUFACTURER_ZIP_CODE, MANUFACTURER_ZIP_CODE_EXT, MANUFACTURER_COUNTRY_CODE, MANUFACTURER_POSTAL_CODE, EXEMPTION_NUMBER, DEVICE_EVENT_KEY, IMPLANT_FLAG, DATE_REMOVED_FLAG, OTHER_ID_NUMBER, DATE_REPORT_y, EVENT_LOCATION, MANUFACTURER_CONTACT_AREA_CODE, MANUFACTURER_CONTACT_AREA_CODE, MANUFACTURER_CONTACT_EXCHANGE, MANUFACTURER_CONTACT_PHONE_NO, MANUFACTURER_CONTACT_PCOUNTRY, MANUFACTURER_G1_ZIP_CODE_EXT, DATE_RETURNED_TO_MANUFACTURER, HEALTH_PROFESSIONAL, INITIAL_REPORT_TO_FDA, DATE_FACILITY_AWARE, REPORT_DATE, REPORT_TO_FDA, DATE_REPORT_TO_FDA, DATE_REPORT_TO_MANUFACTURER, DATE_MANUFACTURER_RECEIVED, DEVICE_DATE_OF_MANUFACTURE, REMOVAL_CORRECTION_NUMBER, PREVIOUS_USE_CODE, SOURCE_TYPE, REPORTER_COUNTRY_CODE, PMA_PMN_NUM, SUPPL_DATES_FDA_RECEIVED, SUPPL_DATES_MFR_RECEIVED, EXPIRATION_DATE_OF_DEVICE, MODEL_NUMBER, CATALOG_NUMBER, LOT_NUMBER, UDI.PUBLIC, UDI.DI, DATE_ADDED, DATE_CHANGED, DATE_RECEIVED_y, DATE_REPORT_x, DATE_OF_EVENT))
final_data_clean <- final_data_clean %>% filter(ADVERSE_EVENT_FLAG != "")
final_data_clean <- final_data_clean %>% filter(PRODUCT_PROBLEM_FLAG != "")
final_data_clean <- final_data_clean %>%
  filter(ADVERSE_EVENT_FLAG == "Y")
final_data_clean <- final_data_clean %>% filter(DEVICE_AGE_TEXT != "")
final_data_clean <- final_data_clean %>% filter(DEVICE_OPERATOR != "")
final_data_clean$DATE_RECEIVED_x <- as.Date(final_data_clean$DATE_RECEIVED_x, format = "%m/%d/%Y")
skim_without_charts(final_data_clean)
```

## Category and sub-category mapping for stent types

```{r}
unique(final_data_clean$GENERIC_NAME)
main_category_mapping <- c("BIFURCATED STENT GRAFT" = "Other Stents",
  "BILIARY STENT SYSTEM FOR BENIGN STRICTURES" = "Other Stents",
  "FGE CATHETER, BILIARY, DIAGNOSTIC - BILIARY STENT - METAL" = "Other Stents",
  "FAD STENT, URETERAL" = "Other Stents",
  "CORONARY DRUG-ELUTING STENT" = "Drug-Eluting Stents (DES)",
  "STENT, CORONARY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",
  "DRUG ELUTING CORONARY STENT DELIVERY SYSTEM" = "Drug-Eluting Stents (DES)", 
  "STENT, INTRACRANIAL NEUROVASCULAR" = "Other Stents", 
  "AFX2 BIFURCATED STENT GRAFT" = "Other Stents",
  "CORONARY STENT DELIVERY SYSTEM" = "Other Stents",
  "STENT, ENDOVASCULAR GRAFT, AORTIC" = "Other Stents",
  "STENT, COLONIC, METALIC, EXPANDABLE" = "Other Stents",
  "NIU STENT, SUPERFICIAL FEMORAL ARTERY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",      
  "BIOMIMICS 3D VASCULAR STENT SYSTEM" = "Other Stents",                       
  "URETERAL STENT" = "Other Stents",                                           
  "MQR STENT, COLONIC METALLIC EXPANDABLE" = "Other Stents",
  "SELF EXPANDING PERIPHERAL STENT SYSTEM" = "Other Stents",                    
  "INTRACRANIAL NEUROVASCULAR STENT" = "Other Stents",                         
  "VASCULAR STENT" = "Other Stents",                                         
  "STENT, ILIAC" = "Other Stents",
  "BARD URETERAL STENT" = "Other Stents",                                     
  "STENT, SUPERFICIAL FEMORAL ARTERY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",         
  "STENT, SUPERFICIAL FEMORAL ARTERY" = "Other Stents",                       
  "STENTS, DRAINS AND DILATORS FOR THE BILIARY DUCTS" = "Other Stents",       
  "STENT, ILIAC VEIN" = "Other Stents",                                       
  "ILIAC COVERED STENT, ARTERIAL" = "Other Stents",                          
  "BIODEGRADABLE POLYMER DRUG ELUTING CORONARY STENT SYSTEM" = "Drug-Eluting Stents (DES)",
  "VASCULAR COVERED STENT" = "Other Stents",                               
  "PERIPHERAL STENT DELIVERY SYSTEM" = "Other Stents",                          
  "STENT, CAROTID" = "Other Stents",                                         
  "STENT, URETERAL" = "Other Stents",                                         
  "FGE STENTS, DRAINS AND DILATORS FOR THE BILIARY DUCTS" = "Other Stents",    
  "VASCULAR STENT GRAFT" = "Other Stents",                                    
  "BALLOON EXPANDABLE VASCULAR COVERED STENT" = "Other Stents",              
  "LIMB STENT GRAFT" = "Other Stents",                                        
  "STENT CORONARY DELIVERY SYSTEM" = "Other Stents",                          
  "MUM STENT, METALIC EXPANDABLE, DUODENAL" = "Other Stents",                  
  "PANCREATIC STENT, COVERED, METALLIC, REMOVABLE" = "Other Stents",          
  "PIPELINE STENT" = "Other Stents",                                           
  "MPR STENT, BLADDER, FETAL" = "Other Stents",                              
  "NIO STENT, ILIAC" = "Other Stents",                                       
  "STENT, CORONARY" = "Other Stents",                                        
  "VELA INFRARENAL STENT GRAFT" = "Other Stents",                             
  "DRUG-ELUTING STENT" = "Drug-Eluting Stents (DES)",                                      
  "VASCULAR STENT SYSTEM" = "Other Stents",                                  
  "URETHRAL STENT" = "Other Stents",                                          
  "VENOUS STENT" = "Other Stents",                                             
  "ENDOVASCULAR STENT DELIVERY SYSTEM" = "Other Stents",                     
  "COVERED CORONARY STENT" = "Other Stents",                                   
  "STENT, ENDOVASCUALR GRAFT, AORTIC" = "Other Stents",                      
  "BILIARY STENT" = "Other Stents",                                           
  "COLONIC STENT" = "Other Stents",                                          
  "STENT, RENAL" = "Other Stents",                                             
  "VENOVO VENOUS STENT" = "Other Stents",                                     
  "TRACHEOBRONCHIAL STENT" = "Other Stents",                                   
  "VASCULAR AND BILIARY STENT" = "Other Stents",                              
  "NIO / STENT, ILIAC" = "Other Stents",                                     
  "MULTIPLE PERIPHERAL ARTERY STENT, BARE-METAL" = "Other Stents",             
  "PYLORIC & DUODENAL STENT" = "Other Stents",                                 
  "CAROTID STENT" = "Other Stents",
  "COVERED CORONARY STENT SYSTEM" = "Other Stents",                            
  "ENDOVASCULAR STENT GRAFT" = "Other Stents",                                
  "DOUBLE LOOP URETERAL STENT" = "Other Stents",                               
  "BALLOON EXPANDABLE STENT" = "Other Stents",                               
  "FLUORO-4¿ COIL SILICONE URETERAL STENT 6CH MULTILENGHT" = "Other Stents",   
  "BIOMIMICS 3D VASCULAR STENT  SYSTEM" = "Other Stents",                     
  "AFX2 BIFRUCATED STENT GRAFT" = "Other Stents",                              
  "UNKNOWN INLAY URETERAL STENT W/ HYDROGLIDE GUIDEWIRE" = "Other Stents",     
  "SINGLE USE BILIARY STENT" = "Other Stents",                                 
  "BARE METAL CORONARY STENT" = "Other Stents",                              
  "DRUG ELUTING STENT" = "Drug-Eluting Stents (DES)",                                      
  "CORONARY DRUG-ELUTING STENT SYSTEM" = "Drug-Eluting Stents (DES)",                    
  "VASULAR STENT" = "Other Stents",                                          
  "INLAY MULTILENGTH URETERAL STENT W GUIDEWIRE" = "Other Stents",          
  "VIABAHN STENT" = "Other Stents",                                            
  "STENT,METALLIC,EXPANDABLE,DUODENAL" = "Other Stents",                       
  "STENT DELIVERY SYSTEM" = "Other Stents",                                    
  "URETERAL STENTS" = "Other Stents",                                        
  "INLAY URETERAL STENT" = "Other Stents",                                     
  "Stent, iliac vein" = "Other Stents",                                       
  "ESOPHAGEAL STENT" = "Other Stents",                                         
  "STENT" = "Other Stents",                                                   
  "VASCULAR COVERED STENT GRAFT" = "Other Stents",                              
  "BALLOON EXPANDABLE BILARY STENT" = "Other Stents",                         
  "BIOMIMICS 3D VASCULAR STENT" = "Other Stents",                              
  "CORONARY DRUG ELUDING STENT" = "Drug-Eluting Stents (DES)",                             
  "VENOVO STENT" = "Other Stents",                                             
  "STENT, VASCULAR, INTRACRANIAL" = "Other Stents",                          
  "BIFURCATED STENT DELIVERY SYSTEM" = "Other Stents",                         
  "MULTIPLE PERIPHERAL ARTERY STENT, BARE METAL" = "Other Stents",           
  "BIFURCATED STENT GRAFT DELIVERY SYSTEM" = "Other Stents",                   
  "ABDOMINAL STENT GRAFT SYSTEM" = "Other Stents",                           
  "STENT SYSTEM" = "Other Stents",                                              
  "PROXIMAL EXTENSION STENT GRAFT" = "Other Stents",                          
  "INTRACRANIAL COIL-ASSIST STENT" = "Other Stents",                           
  "STENT, ENDOVASCULAR GRAFT, AORTIC," = "Other Stents",                    
  "BIFURCATED STENT" = "Other Stents",                                          
  "NIP / STENT, SUPERFICIAL FEMORAL ARTERY" = "Other Stents",                 
  "PRL /  ILIAC COVERED STENT, ARTERIAL" = "Other Stents",                      
  "HYBRID STENT GRAFT, THORACIC AORTIC LESION TREATMENT" = "Other Stents",    
  "Stent, superficial femoral artery, drug-eluting" = "Drug-Eluting Stents (DES)",          
  "STENT., ENDOVASCULAR GRAFT, AORTIC" = "Other Stents",                      
  "DESCENDING THORACIC AORTA ENDOVASCULAR STENT - GRAFT" = "Other Stents",      
  "Stents, drains and dilators for the biliary ducts" = "Other Stents",       
  "BARE-METAL CORONARY ARTERY STENT" = "Other Stents",                         
  "BIOMIIMICS 3D VASCULAR STENT SYSTEM" = "Other Stents",
  "SINGLE USE BILIARY DRAINAGE STENT" = "Other Stents",                         
  "STENT,ENDOVASCULAR GRAFT, AORTIC" = "Other Stents",                        
  "URINARY STENT" = "Other Stents",                                            
  "URINARY DIVERSION STENT" = "Other Stents",                                 
  "NEPHROURETERAL.STENT SYSTEM" = "Other Stents",                             
  "STENT, ENDOVASCULAR GRAFT, AORTA" = "Other Stents",                       
  "STENT, ENDOVASULAR GRAFT, AORTIC" = "Other Stents",                          
  "STENT, ENDOVASCULAR GRAFT, AORTIC." = "Other Stents",                      
  "PERIPHERAL STENT GRAFT" = "Other Stents",                                   
  "POLYMERIC URETERAL STENT" = "Other Stents",                                 
  "5 FR VASCULAR STENT" = "Other Stents",                                      
  "URETER STENT" = "Other Stents",                                             
  "UNKNOWN URETERAL STENT" = "Other Stents",                                   
  "NIN STENT, RENAL" = "Other Stents",                                       
  "BALLOON EXPANDABLE BILIARY STENT" = "Other Stents",                          
  "STENT, ENDOVASCULAR GRAPH, AORTIC" = "Other Stents"
)

subcategory_mapping <- c("BIFURCATED STENT GRAFT" = "Other Stents",
  "BILIARY STENT SYSTEM FOR BENIGN STRICTURES" = "Biliary Stent",
  "FGE CATHETER, BILIARY, DIAGNOSTIC - BILIARY STENT - METAL" = "Biliary Stent",
  "FAD STENT, URETERAL" = "Urological Stent",
  "CORONARY DRUG-ELUTING STENT" = "Drug-Eluting Stents (DES)",
  "STENT, CORONARY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",
  "DRUG ELUTING CORONARY STENT DELIVERY SYSTEM" = "Drug-Eluting Stents (DES)", 
  "STENT, INTRACRANIAL NEUROVASCULAR" = "Intracranial Stent", 
  "AFX2 BIFURCATED STENT GRAFT" = "Other Stents",
  "CORONARY STENT DELIVERY SYSTEM" = "Coronary Stent",
  "STENT, ENDOVASCULAR GRAFT, AORTIC" = "Vascular Stent",
  "STENT, COLONIC, METALIC, EXPANDABLE" = "Gastrointestinal Stent",
  "NIU STENT, SUPERFICIAL FEMORAL ARTERY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",      
  "BIOMIMICS 3D VASCULAR STENT SYSTEM" = "Vascular Stent",                       
  "URETERAL STENT" = "Urological Stent",                                           
  "MQR STENT, COLONIC METALLIC EXPANDABLE" = "Gastrointestinal Stent",
  "SELF EXPANDING PERIPHERAL STENT SYSTEM" = "Peripheral Stent",                    
  "INTRACRANIAL NEUROVASCULAR STENT" = "Intracranial Stent",                         
  "VASCULAR STENT" = "Vascular Stent",                                         
  "STENT, ILIAC" = "Vascular Stent",
  "BARD URETERAL STENT" = "Urological Stent",                                     
  "STENT, SUPERFICIAL FEMORAL ARTERY, DRUG-ELUTING" = "Drug-Eluting Stents (DES)",         
  "STENT, SUPERFICIAL FEMORAL ARTERY" = "Vascular Stent",                       
  "STENTS, DRAINS AND DILATORS FOR THE BILIARY DUCTS" = "Biliary Stent",       
  "STENT, ILIAC VEIN" = "Vascular Stent",                                       
  "ILIAC COVERED STENT, ARTERIAL" = "Vascular Stent",                          
  "BIODEGRADABLE POLYMER DRUG ELUTING CORONARY STENT SYSTEM" = "Drug-Eluting Stents (DES)",
  "VASCULAR COVERED STENT" = "Vascular Stent",                               
  "PERIPHERAL STENT DELIVERY SYSTEM" = "Peripheral Stent",                          
  "STENT, CAROTID" = "Vascular Stent",                                         
  "STENT, URETERAL" = "Urological Stent",                                         
  "FGE STENTS, DRAINS AND DILATORS FOR THE BILIARY DUCTS" = "Biliary Stent",    
  "VASCULAR STENT GRAFT" = "Vascular Stent",                                    
  "BALLOON EXPANDABLE VASCULAR COVERED STENT" = "Vascular Stent",              
  "LIMB STENT GRAFT" = "Other Stents",                                        
  "STENT CORONARY DELIVERY SYSTEM" = "Coronary Stent",                          
  "MUM STENT, METALIC EXPANDABLE, DUODENAL" = "Gastrointestinal Stent",                  
  "PANCREATIC STENT, COVERED, METALLIC, REMOVABLE" = "Biliary Stent",          
  "PIPELINE STENT" = "Other Stents",                                           
  "MPR STENT, BLADDER, FETAL" = "Urological Stent",                              
  "NIO STENT, ILIAC" = "Vascular Stent",                                       
  "STENT, CORONARY" = "Coronary Stent",                                        
  "VELA INFRARENAL STENT GRAFT" = "Urological Stent",                             
  "DRUG-ELUTING STENT" = "Drug-Eluting Stents (DES)",                                      
  "VASCULAR STENT SYSTEM" = "Vascular Stent",                                  
  "URETHRAL STENT" = "Urological Stent",                                          
  "VENOUS STENT" = "Other Stents",                                             
  "ENDOVASCULAR STENT DELIVERY SYSTEM" = "Vascular Stent",                     
  "COVERED CORONARY STENT" = "Coronary Stent",                                   
  "STENT, ENDOVASCUALR GRAFT, AORTIC" = "Vascular Stent",                      
  "BILIARY STENT" = "Biliary Stent",                                           
  "COLONIC STENT" = "Gastrointestinal Stent",                                          
  "STENT, RENAL" = "Urological Stent",                                             
  "VENOVO VENOUS STENT" = "Other Stents",                                     
  "TRACHEOBRONCHIAL STENT" = "Other Stents",                                   
  "VASCULAR AND BILIARY STENT" = "Biliary Stent",                              
  "NIO / STENT, ILIAC" = "Vascular Stent",                                     
  "MULTIPLE PERIPHERAL ARTERY STENT, BARE-METAL" = "Peripheral Stent",             
  "PYLORIC & DUODENAL STENT" = "Gastrointestinal Stent",                                 
  "CAROTID STENT" = "Vascular Stent",
  "COVERED CORONARY STENT SYSTEM" = "Coronary Stent",                            
  "ENDOVASCULAR STENT GRAFT" = "Vascular Stent",                                
  "DOUBLE LOOP URETERAL STENT" = "Urological Stent",                               
  "BALLOON EXPANDABLE STENT" = "Other Stents",                               
  "FLUORO-4¿ COIL SILICONE URETERAL STENT 6CH MULTILENGHT" = "Urological Stent",   
  "BIOMIMICS 3D VASCULAR STENT  SYSTEM" = "Vascular Stent",                     
  "AFX2 BIFRUCATED STENT GRAFT" = "Other Stents",                              
  "UNKNOWN INLAY URETERAL STENT W/ HYDROGLIDE GUIDEWIRE" = "Urological Stent",     
  "SINGLE USE BILIARY STENT" = "Biliary Stent",                                 
  "BARE METAL CORONARY STENT" = "Coronary Stent",                              
  "DRUG ELUTING STENT" = "Drug-Eluting Stents (DES)",                                      
  "CORONARY DRUG-ELUTING STENT SYSTEM" = "Drug-Eluting Stents (DES)",                    
  "VASULAR STENT" = "Vascular Stent",                                          
  "INLAY MULTILENGTH URETERAL STENT W GUIDEWIRE" = "Urological Stent",          
  "VIABAHN STENT" = "Other Stents",                                            
  "STENT,METALLIC,EXPANDABLE,DUODENAL" = "Gastrointestinal Stent",                       
  "STENT DELIVERY SYSTEM" = "Other Stents",                                    
  "URETERAL STENTS" = "Urological Stent",                                        
  "INLAY URETERAL STENT" = "Urological Stent",                                     
  "Stent, iliac vein" = "Vascular Stent",                                       
  "ESOPHAGEAL STENT" = "Gastrointestinal Stent",                                         
  "STENT" = "Other Stents",                                                   
  "VASCULAR COVERED STENT GRAFT" = "Vascular Stent",                              
  "BALLOON EXPANDABLE BILARY STENT" = "Biliary Stent",                         
  "BIOMIMICS 3D VASCULAR STENT" = "Vascular Stent",                              
  "CORONARY DRUG ELUDING STENT" = "Drug-Eluting Stents (DES)",                             
  "VENOVO STENT" = "Other Stents",                                             
  "STENT, VASCULAR, INTRACRANIAL" = "Vascular Stent",                          
  "BIFURCATED STENT DELIVERY SYSTEM" = "Other Stents",                         
  "MULTIPLE PERIPHERAL ARTERY STENT, BARE METAL" = "Peripheral Stent",           
  "BIFURCATED STENT GRAFT DELIVERY SYSTEM" = "Other Stents",                   
  "ABDOMINAL STENT GRAFT SYSTEM" = "Other Stents",                           
  "STENT SYSTEM" = "Other Stents",                                              
  "PROXIMAL EXTENSION STENT GRAFT" = "Other Stents",                          
  "INTRACRANIAL COIL-ASSIST STENT" = "Intracranial Stent",                           
  "STENT, ENDOVASCULAR GRAFT, AORTIC," = "Vascular Stent",                    
  "BIFURCATED STENT" = "Other Stents",                                          
  "NIP / STENT, SUPERFICIAL FEMORAL ARTERY" = "Vascular Stent",                 
  "PRL /  ILIAC COVERED STENT, ARTERIAL" = "Vascular Stent",                      
  "HYBRID STENT GRAFT, THORACIC AORTIC LESION TREATMENT" = "Vascular Stent",    
  "Stent, superficial femoral artery, drug-eluting" = "Drug-Eluting Stents (DES)",          
  "STENT., ENDOVASCULAR GRAFT, AORTIC" = "Vascular Stent",                      
  "DESCENDING THORACIC AORTA ENDOVASCULAR STENT - GRAFT" = "Vascular Stent",      
  "Stents, drains and dilators for the biliary ducts" = "Biliary Stent",       
  "BARE-METAL CORONARY ARTERY STENT" = "Coronary Stent",                         
  "BIOMIIMICS 3D VASCULAR STENT SYSTEM" = "Vascular Stent",
  "SINGLE USE BILIARY DRAINAGE STENT" = "Biliary Stent",                         
  "STENT,ENDOVASCULAR GRAFT, AORTIC" = "Vascular Stent",                        
  "URINARY STENT" = "Urological Stent",                                            
  "URINARY DIVERSION STENT" = "Urological Stent",                                 
  "NEPHROURETERAL.STENT SYSTEM" = "Urological Stent",                             
  "STENT, ENDOVASCULAR GRAFT, AORTA" = "Vascular Stent",                       
  "STENT, ENDOVASULAR GRAFT, AORTIC" = "Vascular Stent",                          
  "STENT, ENDOVASCULAR GRAFT, AORTIC." = "Vascular Stent",                      
  "PERIPHERAL STENT GRAFT" = "Peripheral Stent",                                   
  "POLYMERIC URETERAL STENT" = "Urological Stent",                                 
  "5 FR VASCULAR STENT" = "Vascular Stent",                                      
  "URETER STENT" = "Urological Stent",                                             
  "UNKNOWN URETERAL STENT" = "Urological Stent",                                   
  "NIN STENT, RENAL" = "Urological Stent",                                       
  "BALLOON EXPANDABLE BILIARY STENT" = "Biliary Stent",                          
  "STENT, ENDOVASCULAR GRAPH, AORTIC" = "Vascular Stent"
)

final_data_clean$GENERIC_NAME_main <- main_category_mapping[final_data_clean$GENERIC_NAME]
final_data_clean$GENERIC_NAME_sub <- subcategory_mapping[final_data_clean$GENERIC_NAME]
skim_without_charts(final_data_clean)
```

## Further data cleaning and re-coding variables

```{r}
final_data_clean[c('MANUFACTURER_LINK_FLAG_', 'ADVERSE_EVENT_FLAG', 'PRODUCT_PROBLEM_FLAG', 'REPROCESSED_AND_REUSED_FLAG', 'REPORTER_OCCUPATION_CODE', 'SINGLE_USE_FLAG', 'REMEDIAL_ACTION', 'EVENT_TYPE', 'TYPE_OF_REPORT', 'SUMMARY_REPORT', 'BRAND_NAME', 'MANUFACTURER_D_NAME', 'DEVICE_OPERATOR', 'DEVICE_AVAILABILITY', 'DEVICE_REPORT_PRODUCT_CODE', 'DEVICE_EVALUATED_BY_MANUFACTUR', 'COMBINATION_PRODUCT_FLAG', 'TEXT_TYPE_CODE', 'GENERIC_NAME_main', 'GENERIC_NAME_sub')] <- lapply(final_data_clean[c('MANUFACTURER_LINK_FLAG_', 'ADVERSE_EVENT_FLAG', 'PRODUCT_PROBLEM_FLAG', 'REPROCESSED_AND_REUSED_FLAG', 'REPORTER_OCCUPATION_CODE', 'SINGLE_USE_FLAG', 'REMEDIAL_ACTION', 'EVENT_TYPE', 'TYPE_OF_REPORT', 'SUMMARY_REPORT', 'BRAND_NAME', 'MANUFACTURER_D_NAME', 'DEVICE_OPERATOR', 'DEVICE_AVAILABILITY', 'DEVICE_REPORT_PRODUCT_CODE', 'DEVICE_EVALUATED_BY_MANUFACTUR', 'COMBINATION_PRODUCT_FLAG', 'TEXT_TYPE_CODE', 'GENERIC_NAME_main', 'GENERIC_NAME_sub')], as.factor)

final_data_clean[c('REPORT_SOURCE_CODE')] <- lapply(final_data_clean[c('REPORT_SOURCE_CODE')], as.factor)
final_data_clean[c('MDR_REPORT_KEY')] <- lapply(final_data_clean[c('MDR_REPORT_KEY')], as.factor)
final_data_clean_D <- final_data_clean %>%
  filter(TEXT_TYPE_CODE == "D")
final_data_clean_D <- subset(final_data_clean_D, select = -c(REPORTER_OCCUPATION_CODE, SINGLE_USE_FLAG))
final_data_clean_D <- final_data_clean_D %>% filter(REPROCESSED_AND_REUSED_FLAG != "")
final_data_clean_D <- subset(final_data_clean_D, select = -c(DEVICE_EVALUATED_BY_MANUFACTUR))
final_data_clean_D <- final_data_clean_D %>% filter(COMBINATION_PRODUCT_FLAG != "")
final_data_clean_D <- final_data_clean_D %>% filter(DEVICE_AVAILABILITY != "*")
final_data_clean_D[c('REPORT_SOURCE_CODE','NOE_SUMMARIZED', 'DEVICE_SEQUENCE_NO', 'MDR_TEXT_KEY', 'PATIENT_SEQUENCE_NUMBER')] <- lapply(final_data_clean_D[c('REPORT_SOURCE_CODE', 'NOE_SUMMARIZED', 'DEVICE_SEQUENCE_NO', 'MDR_TEXT_KEY', 'PATIENT_SEQUENCE_NUMBER')], as.factor)
final_data_clean_D <- subset(final_data_clean_D, select = -c(GENERIC_NAME, DEVICE_AGE_TEXT))
final_data_clean_D[c('REPORT_NUMBER')] <- lapply(final_data_clean_D[c('REPORT_NUMBER')], as.factor)
skim_without_charts(final_data_clean_D)
```


```{r}
final_data_clean_unique <- final_data_clean_D %>%
  distinct(MDR_REPORT_KEY, .keep_all = TRUE)
skim_without_charts(final_data_clean_unique)
```

## Initial EDA on cleaned data

```{r}
final_data_clean_unique$Year <- year(final_data_clean_unique$DATE_RECEIVED_x)

yearly_counts <- final_data_clean_unique %>%
  group_by(Year) %>%
  summarise(Count = sum(ADVERSE_EVENT_FLAG=="Y"))

print(yearly_counts)
ggplot(yearly_counts, aes(x = Year, y = Count, fill = Year)) +
  geom_bar(stat = "identity") +
  labs(title = "Year-wise Count of Adverse Events",
       x = "Year",
       y = "Count of Adverse Events") +
  theme_minimal()
```

```{r}
yearly_counts <- final_data_clean_unique %>%
  group_by(Year, EVENT_TYPE) %>%
  summarise(Count = n())

event_type_mapping <- c("D" = "Death", "IN" = "Injury", "M" = "Malfunction")

yearly_counts <- yearly_counts %>%
  mutate(EVENT_TYPE_RENAMED = event_type_mapping[EVENT_TYPE])

print(yearly_counts)

ggplot(yearly_counts, aes(x = Year, y = Count, fill = EVENT_TYPE_RENAMED)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Year-wise Count of Adverse Events by Event Type",
       x = "Year",
       y = "Count of Adverse Events",
       fill = "Event Type") +
  theme_minimal()
```

```{r}
yearly_counts <- final_data_clean_unique %>%
  group_by(Year, GENERIC_NAME_main) %>%
  summarise(Count = n())
# View the aggregated data
print(yearly_counts)
ggplot(yearly_counts, aes(x = Year, y = Count, fill = GENERIC_NAME_main)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Year-wise Count of Adverse Events by Stent Type",
       x = "Year",
       y = "Count of Adverse Events") +
  theme_minimal()
```

```{r}
final_data_clean_unique$YearQuarterShort <- paste(substring(year(final_data_clean_unique$DATE_RECEIVED_x), 3, 4), "Q", quarter(final_data_clean_unique$DATE_RECEIVED_x), sep="-")

quarterly_counts <- final_data_clean_unique %>%
  group_by(YearQuarterShort, GENERIC_NAME_sub) %>%
  summarise(Count = n())

p <- ggplot(quarterly_counts, aes(x = YearQuarterShort, y = Count, color = GENERIC_NAME_sub, group = GENERIC_NAME_sub)) +
  geom_line() +
  geom_point() +
  labs(title = "Quarterly Count of Adverse Events by Stent Sub-type",
       x = "Year-Quarter",
       y = "Count of Adverse Events",
       color = "Generic Name Subcategory") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

p + scale_x_discrete(labels = function(x) gsub("202(\\d)-Q-(\\d)", "\\1-Q-\\2", x))
```

## Saving final dataset to CSV file

```{r}
final_data_clean_unique <- subset(final_data_clean_unique, select = -c(REMEDIAL_ACTION))
skim_without_charts(final_data_clean_unique)
# Save the data frame to a CSV file
write.csv(final_data_clean_unique, file = "final_data_clean_unique.csv", row.names = TRUE)
write.csv(final_data_clean_D, file = "final_data_clean_D.csv", row.names = TRUE)
```

## Identification of Adverse Events 

```{r}
adverse_events <- list(
  "Pain/Discomfort" = c('pain', 'painful', 'hurt', 'hurting', 'ache', 'uneasy', 'discomfort'),
  "Weakness" = c('weak', 'weakness', 'fatigue', 'faintness', 'tired', 'lightheaded', 'dizziness'),
  "Bleeding" = c('bleed', 'bleeding', 'bled', 'blood loss', 'rupture'),
  "Infection" = c('infect', 'infected', 'infection', 'sepsis', 'bacterial', 'viral', 'contaminated', 'contamination', 'fungal'),
  "Device Failure" = c('device fail', 'broken', 'malfunction', 'stent delamination', 'stent leak', 'sent dislodged'),
  "Fatal Outcome" = c('death', 'died', 'expired', 'passed away', 'fatal outcome', 'mortality'),
  "Coronary Issues" = c('thrombosis', 'restenosis', 'ISR', 'occlusion', 'in-stent stenosis', 'in-stent restenosis', 'aneurysm', 'clot'),
  "Heart Issues" = c('clot', 'cardiac arrest', 'heart attack', 'heart failure', 'angina', 'acute coronary syndromes', 'ACS', 'aneurysm'),
  "Respiratory Issues" = c('shortness of breath', 'out of breath', 'respiratory failure', 'respiratory arrest', 'breathing problem', 'dyspnea', 'lung collapse'),
  "Digestive Issues" = c('bowel obstruction', 'constipation', 'bowel issue', 'diarrhea', 'vomit', 'vomiting', 'nausea', 'gastrointestinal bleeding', 'colonic obstruction', 'pancreatitis', 'biliary obstruction'),
  "Surgical Issues" = c('positioning', 'surgical site infection', 'readmission', 'complication', 'postoperative complication', 'misplaced', 'misplacement', 'restent', 'restenting', 'internal bleeding', 'shock', 'leakage', 'leak'),
  "Psychological Issues" = c('distress', 'cognitive impairment', 'cognitive dysfunction', 'cognitive', 'anxiety', 'depression')
)

results <- data.frame(
  AdverseEvent = character(),
  TotalOccurrences = integer(),
  UniqueReports = integer(),
  PercentageReports = numeric(),
  stringsAsFactors = FALSE
)

total_reports <- n_distinct(final_data_clean_unique$MDR_REPORT_KEY)

for (event in names(adverse_events)) {
  keywords <- adverse_events[[event]]
  keyword_pattern <- paste(keywords, collapse = "|")
  
  total_occurrences <- sum(str_count(final_data_clean_unique$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE)))
  
  # Count unique reports
  unique_reports <- n_distinct(final_data_clean_unique$MDR_REPORT_KEY[str_detect(final_data_clean_unique$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE))])
  
  # Calculate the percentage of reports
  percentage_reports <- (unique_reports / total_reports) * 100
  
  # Append results
  results <- rbind(results, data.frame(
    AdverseEvent = event,
    TotalOccurrences = total_occurrences,
    UniqueReports = unique_reports,
    PercentageReports = round(percentage_reports, 2)
  ))
}

# Display the results in a properly formatted table
results %>%
  kable(col.names = c("Adverse Event", "Total Occurrences", "Unique Reports", "Percentage of Reports (%)")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## EDA of AEs over time

```{r}
quarterly_counts <- data.frame(
  YearQuarterShort = character(),
  AdverseEvent = character(),
  TotalOccurrences = integer(),
  stringsAsFactors = FALSE
)

unique_quarters <- unique(final_data_clean_unique$YearQuarterShort)

for (quarter in unique_quarters) {
  data_quarter <- final_data_clean_unique %>% filter(YearQuarterShort == quarter)
  
  for (event in names(adverse_events)) {
    keywords <- adverse_events[[event]]
    keyword_pattern <- paste(keywords, collapse = "|")
    
    total_occurrences <- sum(str_count(data_quarter$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE)))
    
    quarterly_counts <- rbind(quarterly_counts, data.frame(
      YearQuarterShort = quarter,
      AdverseEvent = event,
      TotalOccurrences = total_occurrences
    ))
  }
}

quarterly_counts$YearQuarterShort <- factor(quarterly_counts$YearQuarterShort, levels = unique(sort(quarterly_counts$YearQuarterShort)))

total_occurrences <- quarterly_counts %>%
  group_by(AdverseEvent) %>%
  summarise(Total = sum(TotalOccurrences)) %>%
  arrange(desc(Total))

top_5_events <- total_occurrences %>% top_n(5, Total) %>% pull(AdverseEvent)

quarterly_counts_top5 <- quarterly_counts %>% filter(AdverseEvent %in% top_5_events)
quarterly_counts_remaining <- quarterly_counts %>% filter(!AdverseEvent %in% top_5_events)

total_reports <- quarterly_counts %>%
  group_by(AdverseEvent) %>%
  summarise(TotalReports = sum(TotalOccurrences))

quarterly_counts <- quarterly_counts %>%
  left_join(total_reports, by = "AdverseEvent") %>%
  mutate(RelativeFrequency = TotalOccurrences / TotalReports)

quarterly_counts_top5_rf <- quarterly_counts %>% filter(AdverseEvent %in% top_5_events)
quarterly_counts_remaining_rf <- quarterly_counts %>% filter(!AdverseEvent %in% top_5_events)

plot_top5 <- ggplot(quarterly_counts_top5, aes(x = YearQuarterShort, y = TotalOccurrences, color = AdverseEvent, group = AdverseEvent)) +
  geom_line() +
  geom_point() +
  labs(title = "Total Mentions of Top 5 Adverse Events",
       x = "Year-Quarter",
       y = "Total Mentions") +
  theme_minimal() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_discrete(limits = levels(quarterly_counts$YearQuarterShort))

plot_remaining <- ggplot(quarterly_counts_remaining, aes(x = YearQuarterShort, y = TotalOccurrences, color = AdverseEvent, group = AdverseEvent)) +
  geom_line() +
  geom_point() +
  labs(title = "Total Mentions of Low Occurring Adverse Events",
       x = "Year-Quarter",
       y = "Total Mentions") +
  theme_minimal() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_discrete(limits = levels(quarterly_counts$YearQuarterShort))

plot_top5_rf <- ggplot(quarterly_counts_top5_rf, aes(x = YearQuarterShort, y = RelativeFrequency, color = AdverseEvent, group = AdverseEvent)) +
  geom_line() +
  geom_point() +
  labs(title = "Proportion of Top 5 Adverse Events",
       x = "Year-Quarter",
       y = "Proportion") +
  theme_minimal() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_discrete(limits = levels(quarterly_counts$YearQuarterShort))

plot_remaining_rf <- ggplot(quarterly_counts_remaining_rf, aes(x = YearQuarterShort, y = RelativeFrequency, color = AdverseEvent, group = AdverseEvent)) +
  geom_line() +
  geom_point() +
  labs(title = "Proportion of Low Occurring Adverse Events",
       x = "Year-Quarter",
       y = "Proportion") +
  theme_minimal() +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  scale_x_discrete(limits = levels(quarterly_counts$YearQuarterShort))

print(plot_top5)
print(plot_remaining)
print(plot_top5_rf)
print(plot_remaining_rf)
```

## Free text analysis (generating wordclounds based on stent types)

```{r}
preprocess_text <- function(text, custom_stopwords = c()) {
  text <- tolower(text) 
  text <- removePunctuation(text) 
  text <- removeNumbers(text) 
  stop_words <- c(stopwords("en"), custom_stopwords)
  text <- removeWords(text, stop_words) 
  text <- stripWhitespace(text) 
  return(text)
}

custom_stopwords <- c("patient", "patients", "stent", "device", "using", "due", "used", "noted", "unknown", "physician", "xmm", "stenting", "across", "system", "reported", "two", "devices", "stents", "event", "another", "using", "des", "however", "yes", "aaa", "performed", "provide", "provided", "procedure")

final_data_clean_unique$FOI_TEXT <- preprocess_text(final_data_clean_unique$FOI_TEXT, custom_stopwords)

stent_sub_types <- unique(final_data_clean_unique$GENERIC_NAME_sub)

graphics.off()
par(mfrow = c(1, 1))

for (sub_type in stent_sub_types) {
  print(paste("Processing subtype:", sub_type)) 

  
  sub_type_data <- final_data_clean_unique %>% filter(GENERIC_NAME_sub == sub_type)
  
  
  if (nrow(sub_type_data) == 0) {
    message(paste("No data for subtype:", sub_type))
    next
  }
  
  text_corpus <- paste(sub_type_data$FOI_TEXT, collapse = " ")
  
  corpus <- Corpus(VectorSource(text_corpus))
  
  wordcloud(corpus, 
            scale = c(2, 0.5),   
            max.words = 50,      
            random.order = FALSE,
            colors = brewer.pal(8, "Dark2"))
  
  title(main = paste(sub_type))
  
}
graphics.off()
```

```{r}
peripheral_data <- final_data_clean_unique %>% filter(GENERIC_NAME_sub == "Peripheral Stent")

peripheral_data$FOI_TEXT <- preprocess_text(peripheral_data$FOI_TEXT, custom_stopwords)

text_corpus <- paste(peripheral_data$FOI_TEXT, collapse = " ")

corpus <- Corpus(VectorSource(text_corpus))

wordcloud(corpus, 
          scale = c(2, 0.5),    
          max.words = 50,      
          random.order = FALSE,
          colors = brewer.pal(8, "Dark2"))
title(main = paste("Peripheral Stent"))
```

## Exploring AEs by stent types

```{r}
event_stent_counts <- data.frame(
  AdverseEvent = character(),
  StentSubType = character(),
  Count = integer(),
  stringsAsFactors = FALSE
)

for (event in names(adverse_events)) {
  keywords <- adverse_events[[event]]
  keyword_pattern <- paste(keywords, collapse = "|")
  
  for (sub_type in unique(final_data_clean_unique$GENERIC_NAME_sub)) {
    sub_type_data <- final_data_clean_unique %>% filter(GENERIC_NAME_sub == sub_type)
    
    total_occurrences <- sum(str_count(sub_type_data$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE)))
    
    event_stent_counts <- rbind(event_stent_counts, data.frame(
      AdverseEvent = event,
      StentSubType = sub_type,
      Count = total_occurrences
    ))
  }
}

ggplot(event_stent_counts, aes(x = AdverseEvent, y = Count, fill = StentSubType)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Adverse Events by Stent Subtype",
       x = "Adverse Event",
       y = "Count",
       fill = "Stent Subtype") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}
event_stent_counts <- data.frame(
  AdverseEvent = character(),
  StentSubType = character(),
  Count = integer(),
  stringsAsFactors = FALSE
)

for (event in names(adverse_events)) {
  keywords <- adverse_events[[event]]
  keyword_pattern <- paste(keywords, collapse = "|")
  
  for (sub_type in unique(final_data_clean_unique$GENERIC_NAME_sub)) {
    sub_type_data <- final_data_clean_unique %>% filter(GENERIC_NAME_sub == sub_type)
    
    total_occurrences <- sum(str_count(sub_type_data$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE)))
    
    event_stent_counts <- rbind(event_stent_counts, data.frame(
      AdverseEvent = event,
      StentSubType = sub_type,
      Count = total_occurrences
    ))
  }
}

total_occurrences_by_subtype <- event_stent_counts %>%
  group_by(StentSubType) %>%
  summarise(Total = sum(Count))

event_stent_counts <- event_stent_counts %>%
  left_join(total_occurrences_by_subtype, by = "StentSubType") %>%
  mutate(Proportion = Count / Total)

ggplot(event_stent_counts, aes(x = AdverseEvent, y = Proportion, fill = StentSubType)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "Proportion of Adverse Events by Stent Subtype",
       x = "Adverse Event",
       y = "Proportion",
       fill = "Stent Subtype") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
#Part-B Analysis
## PRR Analysis using Coronary Stent as reference

```{r}
event_stent_counts <- data.frame(
  AdverseEvent = character(),
  StentSubType = character(),
  Count = integer(),
  stringsAsFactors = FALSE
)

# Count AE occurrences for each stent subtype
for (event in names(adverse_events)) {
  keywords <- adverse_events[[event]]
  keyword_pattern <- paste(keywords, collapse = "|")
  
  for (sub_type in unique(final_data_clean_unique$GENERIC_NAME_sub)) {
    sub_type_data <- final_data_clean_unique %>% filter(GENERIC_NAME_sub == sub_type)
    
    # Count occurrences of AE in the text column
    total_occurrences <- sum(str_count(sub_type_data$FOI_TEXT, regex(keyword_pattern, ignore_case = TRUE)))
    
    # Append counts to the event_stent_counts dataframe
    event_stent_counts <- rbind(event_stent_counts, data.frame(
      AdverseEvent = event,
      StentSubType = sub_type,
      Count = total_occurrences
    ))
  }
}

event_stent_counts <- event_stent_counts %>%
  group_by(StentSubType) %>%
  mutate(
    TotalAE = sum(Count),    
    Other_AE = TotalAE - Count 
  ) %>%
  ungroup()

reference_stent <- "Coronary Stent"

reference_counts <- event_stent_counts %>%
  filter(StentSubType == reference_stent) %>%
  group_by(AdverseEvent) %>%
  summarize(
    a_ref = sum(Count),                    
    b_ref = sum(TotalAE) - a_ref          
  )

prr_calculate <- event_stent_counts %>%
  filter(StentSubType != reference_stent) %>%
  group_by(AdverseEvent, StentSubType) %>%
  summarize(
    a_test = sum(Count),                   
    b_test = sum(TotalAE) - a_test        
  ) %>%
  left_join(reference_counts, by = "AdverseEvent") %>%
  mutate(
    PRR = ifelse((a_test > 0 & b_test > 0 & a_ref > 0 & b_ref > 0), 
                 (a_test / (a_test + b_test)) / (a_ref / (a_ref + b_ref)), 
                 NA)
  )

```

## Fisher's text for validation

```{r}
prr_valid <- prr_calculate %>%
  filter(!is.na(PRR))

perform_fisher_test <- function(a_test, b_test, a_ref, b_ref) {
  matrix <- matrix(c(a_test, b_test, a_ref, b_ref), nrow = 2)
  test_result <- fisher.test(matrix)
  return(test_result$p.value)
}

final_table <- prr_valid %>%
  rowwise() %>%
  mutate(
    fisher_p = perform_fisher_test(a_test, b_test, a_ref, b_ref)
  ) %>%
  ungroup()

write.csv(final_table, "final_prr_fisher_table.csv", row.names = FALSE)

print(final_table)

```

## Visualise significant PRR and Fisher's results

```{r}
# Filter out PRRs with p-value >= 0.05
filtered_data <- final_table %>%
  filter(fisher_p < 0.05, PRR > 1)

ggplot(filtered_data, aes(x = AdverseEvent, y = PRR, fill = StentSubType)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  labs(title = "PRR by Adverse Event and Stent Sub-type (p < 0.05, PRR>1)", 
       x = "Adverse Event", 
       y = "Proportional Reporting Ratio (PRR)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1") 

```

## Unsupervised emotion detection using NRC emotion lexicon

```{r}
# Apply emotion detection using the 'get_nrc_sentiment' function from syuzhet
emotion_data <- get_nrc_sentiment(final_data_clean_unique$FOI_TEXT)

# Display the first few rows of the emotion data
head(emotion_data)

# Add the emotion data to the existing dataset
final_data_with_emotions <- cbind(final_data_clean_unique, emotion_data)

# Summarize the predominant emotion for each entry
final_data_with_emotions <- final_data_with_emotions %>%
  rowwise() %>%
  mutate(
    predominant_emotion = names(emotion_data)[which.max(c_across(anger:trust))]
  ) %>%
  ungroup()

# View the updated data with predominant emotions
head(final_data_with_emotions)

# Summarize emotion counts for the predominant emotions
emotion_summary <- final_data_with_emotions %>%
  group_by(predominant_emotion) %>%
  summarise(count = n(), .groups = 'drop')

# Print emotion summary
print(emotion_summary)

# Optionally, plot the distribution of predominant emotions
barplot(emotion_summary$count, names.arg = emotion_summary$predominant_emotion,
        main = "Distribution of Predominant Emotions", col = rainbow(length(emotion_summary$count)), las = 2)

```

## Get the quarterly trend of predominant emotions

```{r}
# Summarize the counts of predominant emotions for each quarter
quarterly_predominant_emotion_trend <- final_data_with_emotions %>%
  group_by(YearQuarterShort, predominant_emotion) %>%
  summarise(count = n(), .groups = 'drop')

# View the summarized quarterly predominant emotion trend
print(quarterly_predominant_emotion_trend)

# Reshape the data for easier plotting
quarterly_predominant_emotion_long <- quarterly_predominant_emotion_trend %>%
  pivot_wider(names_from = predominant_emotion, values_from = count, values_fill = 0)

# Reshape the data to long format for ggplot
quarterly_predominant_emotion_long <- quarterly_predominant_emotion_long %>%
  pivot_longer(cols = -YearQuarterShort, names_to = "PredominantEmotion", values_to = "Count")

# Plot the trend of the predominant emotions over the quarters
ggplot(quarterly_predominant_emotion_long, aes(x = YearQuarterShort, y = Count, color = PredominantEmotion, group = PredominantEmotion)) +
  geom_line(size = 1) +
  labs(title = "Quarterly Trend of Predominant Emotions", x = "Quarter", y = "Emotion Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust x-axis text for better readability
```

## Logistic regression on Infection for further validation

```{r}
infection_keywords <- c('infect', 'infected', 'infection', 'sepsis', 'bacterial', 'viral', 'contaminated', 'contamination', 'fungal') 
infection_pattern <- paste(infection_keywords, collapse = "|")

final_data_with_emotions <- final_data_with_emotions %>%
  mutate(Infection = ifelse(str_detect(FOI_TEXT, regex(infection_pattern, ignore_case = TRUE)), 1, 0))

# Set the reference level for StentSubType to the type you'd like to compare others against (e.g., "Coronary Stent")
final_data_with_emotions$GENERIC_NAME_sub <- relevel(final_data_with_emotions$GENERIC_NAME_sub, ref = "Coronary Stent")

# Fit the logistic regression model
logistic_model_infection <- glm(Infection ~ GENERIC_NAME_sub, data = final_data_with_emotions, family = binomial)

# View the summary to see the significance of each stent type
summary(logistic_model_infection)
exp(coef(logistic_model_infection))
```

## Logistic regression on Digestive Issues for further validation

```{r}
digestive_keywords <- c('bowel obstruction', 'constipation', 'bowel issue', 'diarrhea', 'vomit', 'vomiting', 'nausea', 'gastrointestinal bleeding', 'colonic obstruction', 'pancreatitis', 'biliary obstruction') 
digestive_pattern <- paste(digestive_keywords, collapse = "|")

final_data_with_emotions <- final_data_with_emotions %>%
  mutate(Digestive_Issues = ifelse(str_detect(FOI_TEXT, regex(digestive_pattern, ignore_case = TRUE)), 1, 0))

final_data_with_emotions$GENERIC_NAME_sub <- relevel(final_data_with_emotions$GENERIC_NAME_sub, ref = "Coronary Stent")

# Fit the logistic regression model
logistic_model_digestive <- glm(Digestive_Issues ~ GENERIC_NAME_sub, data = final_data_with_emotions, family = binomial)

# View the summary to see the significance of each stent type
summary(logistic_model_digestive)
exp(coef(logistic_model_digestive))
```

## Save the final dataset with emotions

```{r}
write.csv(final_data_with_emotions, "final_data_with_emotions.csv", row.names = FALSE)
```

